### 2021-09-01 documentos/math.tex
Avance N=1

>>>>

This part is devoted to derive the set of conditions a Pauli map need to satisfy to fulfill the CP condition i.e. all the eigenvalues of the Choi matrix associated to the channel must be non-negative. First we obtain the set of inequalities for a single qubit Pauli channel and then we extend the results for the general case of $N$ qubits.

\subsubsection{Single qubit Pauli channels}

\afnote{Notación para matrices densidad vectorizadas? $\varrho$ ?}

By writing the elements of the density matrix in vector form $\varrho=\left(\varrho_0,\varrho_1,\varrho_2,\varrho_3\right)^{\intercal}$, the action of a Pauli map on $\varrho$ for a single qubit may be written as $\varrho \to \varrho'=\hat \mcE \varrho$, where $\hat \mcE$ is the matrix representation of the map. Moreover it can be shown that in the Pauli basis $(\sigma_0,\sigma_1,i\sigma_2,\sigma_3)$, $\hat \mcE$ reduces simply to $\mathrm{diag}\left(\tau_0,\tau_1,\tau_2,\tau_3\right)$.

Let reorganize the elements of the Pauli basis as $(\sigma_0,\sigma_3,\sigma_1,i\sigma_2)$, in this way it is possible to write the matrix representation of the map as $\hat \mcE = \tau_{03} \oplus \tau_{12}$, where $\tau_{jk}=\mathrm{diag}\left(\tau_j,\tau_k\right)$ and the symbol $``\oplus "$ represents a direct sum of matrices. The advantage of this ordering is manifested when the matrix $\hat \mcE$ is transformed to the computational basis $(u_{00},u_{11},u_{01},u_{10})$, $\hat \mcE_c$:
% 
\begin{align}
 \hat \mcE_c =& \left(H\oplus H\right)\hat \mcE \left(H\oplus H\right)^{\intercal}\\
 =& \left(H\oplus H\right) \left(\tau_{03} \oplus \tau_{12}\right)\left(H\oplus H\right)^{\intercal}\\
 =& H\tau_{03}H \oplus H\tau_{12}H\\
 =&\begin{pmatrix}
        \tau_0+\tau_3 & \tau_0-\tau_3\\
        \tau_0-\tau_3 & \tau_0+\tau_3\\
        &&\tau_0+\tau_3 & \tau_0-\tau_3\\
        &&\tau_0-\tau_3 & \tau_0+\tau_3\\        
    \end{pmatrix},
 \label{Eq_E_P_C}
\end{align}
% 
where $H$ is the Haddamard matrix
% 
\begin{equation}
 H=\begin{pmatrix}
        1 & 1\\
        1 & -1\\
    \end{pmatrix}.
 \label{Hadd_Mat}
\end{equation}
% 
After applying the reshuffling operation on $\hat \mcE_c$, we get the associated Choi matrix (or sometimes called dynamical matrix) of the map $D$, it reads
% 
\begin{equation}
 D=\begin{pmatrix}
        \tau_0+\tau_3 & \tau_1+\tau_2\\
        \tau_1+\tau_2 & \tau_0+\tau_3\\
        &&\tau_0-\tau_3 & \tau_1-\tau_2\\
        &&\tau_1-\tau_2 & \tau_0-\tau_3\\        
    \end{pmatrix}.
 \label{Eq_D_P}
\end{equation}
% 
Back to the Pauli basis, the Choi matrix holds
\begin{align}
 D_p =& \left(\frac{1}{2}H\oplus H\right)\hat D \left(\frac{1}{2}H\oplus H\right)^{\intercal}\\
 =&\frac{1}{4}\left(H\oplus H\right)\hat D \left(H\oplus H\right)^{\intercal}\\
=&\begin{pmatrix}
        \lambda_0\\
        &\lambda_1\\
        &&\lambda_2\\
        &&&\lambda_3\\
    \end{pmatrix}.
%   =&\begin{pmatrix}
%         \tau_0+\tau_3+\tau_1+\tau_2\\
%         &\tau_0-\tau_3+\tau_1-\tau_2\\
%         &&\tau_0+\tau_3-\tau_1-\tau_2\\
%         &&&\tau_0-\tau_3-\tau_1+\tau_2\\        
%     \end{pmatrix}.
 \label{Eq_D_C_P}
\end{align}
% 
In other words, the Pauli basis diagonalizes the Choi matrix associated to any Pauli map, with eigenvalues related to the map coefficients $\tau$ as
% 
\begin{equation}
\begin{pmatrix}
        \lambda_0\\
        \lambda_1\\
        \lambda_2\\
        \lambda_3\\   
    \end{pmatrix}
 =\frac{1}{2}\begin{pmatrix}
        1&1&1&1\\
        1&-1&1&-1\\
        1&1&-1&-1\\
        1&-1&-1&1\\
    \end{pmatrix}
    \begin{pmatrix}
        \tau_0\\
        \tau_3\\
        \tau_1\\
        \tau_2\\   
    \end{pmatrix},
 \label{Eigen1}
\end{equation}
% 
or in a compact form
% 
\begin{equation}
 \lambda = \frac{1}{2}H\otimes H \tau.
\end{equation}
% 
Now we proceed to generalize this result for the case $N$ qubits case.

\subsubsection{$N$ qubits}

Coming soon...

\subsection{Parte de Francois}
